Numerical modelling of the Cordilleran ice sheet

### 2014-08-08 kappa.tex
Replace "I" by "J. Seguinot" in author contrib.

\noindent\textbf{Author contributions}
\footnotesize{\begin{paper}
  \item[I] A.~P.~Stroeven initiated the Cordilleran ice sheet modelling
project; I set-up the ice sheet model (PISM) and supercomputing workflow, ran
simulations and wrote the first draft; C.~Khroulev implemented necessary code
changes in the model; I.~Rogozhina contributed to experiment design; A.~P.~Stroeven
helped with interpretation of the results; and Q.~Zhang prepared some of the
forcing data. All co-authors contributed to improve the text.
  \item[II] I analysed the weather data, wrote the positive degree day model
(PyPDD), ran computations and wrote the manuscript. A.~P.~Stroeven contributed
with editorial comments at the pre-submission stage and I.~Rogozhina helped to
assess the reviews.
  \item[III] I.~Rogozhina provided the original idea; I analysed the weather
data and developed a new parameterization of daily temperature standard
deviation. I.~Rogozhina and I wrote the manuscript. A.~P.~Stroeven contributed
with editorial comments at the pre-submission stage.
  \item[IV] I integrated the new parameterization of standard deviation into
PISM, ran the simulations and wrote the first draft; I.~Rogozhina guided
experiment design; A.~P.~Stroeven, M.~Margold and J.~Kleman took part in the
interpretation and comparison of model results against geological evidence. All
co-authors contributed to improve the text.
\end{paper}}

>>>>

\noindent\textbf{Author contributions}
\footnotesize{\begin{paper}
  \item[I] A.~P.~Stroeven initiated the Cordilleran ice sheet modelling
project; J.~Seguinot set-up the ice sheet model (PISM) and supercomputing
workflow, ran simulations and wrote the first draft; C.~Khroulev implemented
necessary code changes in the model; I.~Rogozhina contributed to experiment
design; A.~P.~Stroeven helped with interpretation of the results; and Q.~Zhang
prepared some of the forcing data. All co-authors contributed to improve the
text.
  \item[II] J.~Seguinot analysed the weather data, wrote the positive degree
day model (PyPDD), ran computations and wrote the manuscript. A.~P.~Stroeven
contributed with editorial comments at the pre-submission stage and
I.~Rogozhina helped to assess the reviews.
  \item[III] I.~Rogozhina provided the original idea; J.~Seguinot analysed the
weather data and developed a new parameterization of daily temperature standard
deviation. I.~Rogozhina and J.~Seguinot wrote the manuscript. A.~P.~Stroeven
contributed with editorial comments at the pre-submission stage.
  \item[IV] J.~Seguinot integrated the new parameterization of standard
deviation into PISM, ran the simulations and wrote the first draft;
I.~Rogozhina guided experiment design; A.~P.~Stroeven, M.~Margold and J.~Kleman
took part in the interpretation and comparison of model results against
geological evidence. All co-authors contributed to improve the text.
\end{paper}}
